Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-12-07 vesicle_code/docs/permeableVes/main.tex
working on figs
yny

\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.  
For example, erythrocytes demonstrate efficient exchange of water to participate in efficient body water homeostasis \cite{SugieIntaglietta2018_AmJPhysiolHCP}.
The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
In the presence of osmolarity (a contrast in the concentration of a solute impermeable to the membrane), water flows in or out of the membrane to adjust the interior cellular volume. In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while for an artificial lipid bilayer membrane the water permeability is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS}.

 Most modeling of water transport across the membrane focuses on the water flux due to osmolarity. However, the osmotic flux is inevitably coupled with the mechanical effects for a deformable membrane \cite{yao-mor2017}.

>>>>

\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}.  
For example, erythrocytes demonstrate efficient exchange of water to participate in efficient body water homeostasis \cite{SugieIntaglietta2018_AmJPhysiolHCP}. Another example is the regulation of cell volume and the cell membrane tension in cell migration \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS}.
The cell membrane is permeable to water and water-soluble molecules \cite{Dick1964_JTB,FettiplaceHaydon1980_PhysRev,DeamerBramhall1986_ChemPhysLipids,Grafmueller2019_ABLS}.
In the presence of osmolarity (a contrast in the concentration of a solute impermeable to the membrane), water flows in or out of the membrane to adjust the interior cellular volume. In the red blood cell membrane, aquaporin-1 (AQP1) channels give rise to a much higher water permeability of $\sim 1.8\times 10^{-2}$ cm/s in erythrocytes \cite{YangMaVerkman2001_JBC} while for an artificial lipid bilayer membrane the water permeability is in the range of $10^{-4}-10^{-3}$ cm/s \cite{ThompsonHuang1966_ANYAS,FettiplaceHaydon1980_PhysRev,Grafmueller2019_ABLS,Dimova2020_GVB}.

Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB}. Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}. 
In these situations, the osmolarity is the main drive for water transport across the membrane. Thus most modeling works ignore the mechanical effects (capillary pressure, bending force and membrane tension) on vesicles under an osmotic stress. 
However, the osmotic water flux is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.
